\documentclass[
  aps,
  prd,
  onecolumn,
  notitlepage,
  nofootinbib,
  superscriptaddress,
  10pt
]{revtex4-2}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\usepackage{amsmath,amssymb,amsfonts,mathtools,mathrsfs,bm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}
\usepackage{booktabs}
\usepackage{pifont}
\usepackage{tikz}
\usetikzlibrary{positioning, arrows.meta, decorations.pathreplacing, calc, backgrounds}
\usepackage{amsthm}
\usepackage{braket}
\newcommand{\ketbra}[2]{\mathinner{|{#1}\rangle\,\langle{#2}|}}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage[shortlabels]{enumitem}
\setlist[enumerate]{align=left,labelindent=0pt}
\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=blue}
\usepackage{subfig}
\usepackage{physics}
\usepackage{siunitx}
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=magenta,urlcolor=blue}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{remark}{Remark}[section]
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{axiom}{Axiom}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{statement}{Statement}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{postulate}{Postulate}[section]
\newtheorem{assumption}{Assumption}[section]
\newtheorem{conjecture}{Conjecture}[section]
\newtheorem{example}{Example}[section]
\newcommand{\AdS}{\mathrm{AdS}}
\newcommand{\dS}{\mathrm{dS}}
\newcommand{\Weyl}{\mathrm{Weyl}}
\newcommand{\IR}{\mathrm{IR}}
\newcommand{\UV}{\mathrm{UV}}
\newcommand{\ren}{\mathrm{ren}}
\newcommand{\SK}{\mathrm{SK}}
\newcommand{\bulk}{\mathrm{bulk}}
\IfFileExists{macros_2t.tex}{%
  \input{macros_2t}%
}{%
  \IfFileExists{Main/macros_2t.tex}{%
    \input{Main/macros_2t}%
  }{%
    \input{../Main/macros_2t}%
  }%
}

\makeatletter
\def\do@check@aux{}%
\AtBeginDocument{\def\do@check@aux{}}
\def\check@aux{\immediate\closeout\@mainaux}%
\makeatother

\begin{document}

\title{Emergence of spinor symmetry and supersymmetry from mixing of two bosonic times in generic $AdS_5$}
\author{Dmytro Surdu}
\email{lanceoflife@gmail.com}
\date{\today}

\begin{abstract}
We study when the \(\mathbb Z_2\) holonomy identified in the limited-scope two-time theorem is realized as a genuine odd symmetry on the \(AdS_5\) boundary. The setting has two bosonic times---physical time and renormalization-group time---and assumes a local Schwinger--Keldysh bicomplex on sufficiently local observables, the limited-scope holonomy package, an RG-monotone/anomalous-descent package, parity transport together with a same-tick selected-line obstruction supplement and a delayed selected-line supplement at the successor step, a Peierls bracket, energy/covariance control, and a UV conformal common sector. Under these hypotheses, RG time produces an odd first-descendant class on the boundary. The limited-scope square-loop is transported to a sign action on a same-tick selected quotient image, while the delayed selected-line supplement furnishes a nonzero quotient point at the successor step. These two selected-line interfaces supply the nonvanishing input needed for canonicalization, so the odd class is nonzero and admits a unique canonical representative \(\mathcal J^{\mathrm{can}}_{\Lambda_k}\). Its Peierls Hamiltonian action defines a nontrivial local \(\Gamma\)-odd derivation \(\delta_{\Lambda_k}=\{\mathcal J^{\mathrm{can}}_{\Lambda_k},-\}_{\mathrm P,\Lambda_k}\). Using AQFT reconstruction together with the Haag--\L opusza\'nski--Sohnius theorem, we obtain a finite-dimensional Weyl-spinor odd charge module on the UV vacuum representation. Combining this odd sector with the common conformal sector yields the full four-dimensional superconformal algebra on the same Hilbert space: \(\mathfrak{su}(2,2|N)\) for \(N\neq4\), and \(\mathfrak{psu}(2,2|4)\) in the \(N=4\) case after the standard central quotient. A separate strengthened set of assumptions provides an optional criterion selecting \(N=4\). The result gives a theorem-level route from bosonic two-time data to boundary spinorial and superconformal structure.
\end{abstract}

\maketitle

\section{Introduction}
\label{sec:intro}

We propose a framework in which the questions ``why anything would happen''
(against the constant von Neumann entropy wall of unitary \(AdS/CFT\)) and
``why anything (in the sense of matter origin) would exist'' can be considered
together. This paper should be read together with its companion paper on Two Times Limited Scope Theorem (2T-LS)~\cite{Surdu2TLSLetter2026}, which we recommend reading first.

The common structural theme arises when \(AdS_5/CFT_4\) satisfies the assumptions of Two Times Main Theorem (2T-Main). The theorem then shows that, in such a two-time setting, the assumptions force structural components that induce an intrinsic odd sector whose realization has both dynamical consequences for time and symmetry consequences for matter.
It is shown in 2T-LS that the classical ledger within broad unitary microscopic dynamics induces both fundamental \(Z_2\)-gradedness with cochain-level \(d^2=0\) and a genuine distinction between ``before'' and ``after''. In this paper, we show that 2T-Main establishes spinor symmetry and superconformal boundary structure and, conjecturally, points toward a microscopic Type IIB realization.  The further layout addresses the theorem-level realization problem inside this broader framework.

At theorem level the proposed 2T program has two stages.  The first asks whether a two-time
structure carries an intrinsic odd holonomy at all.  The Limited Scope theorem
answers that question affirmatively: the square-loop has odd parity, the
induced \(\mathbb Z_2\)-cover does not split, and a detector makes the
holonomy operationally distinguishable.  The second
stage asks when that odd holonomy survives the boundary reduction
steps and becomes a genuine local odd channel with symmetry consequences.  That
second-stage realization problem is the subject of the present paper.

This distinction is essential.  The Limited Scope theorem is a broad
obstruction theorem.  By itself it does not produce a sufficiently local odd
generator, a Hilbert-space odd implementer, a Weyl-spinor transformation law,
or a superalgebra.  The theorem proved here is more physical: it
singles out the class of \(AdS_5\) boundary theories in which the LS odd
holonomy reaches the renormalization-group anomaly sector, survives the local
descendant quotient, remains visible on local probes, and can therefore be
promoted to a genuine odd symmetry derivation.

\subsection{Landscape}

The present work sits at the intersection of several literatures that are
usually discussed separately.  Standard \(AdS/CFT\) and holographic
renormalization relate radial evolution to boundary renormalization-group
structure and organize how conformal anomalies, counterterms, and boundary data
are encoded in the bulk/boundary dictionary
~\cite{Maldacena1998,GubserKlebanovPolyakov1998,Witten1998AdSCFT,HenningsonSkenderis1998,deHaroSkenderisSolodukhin2001,Skenderis2002HR}.
Lorentzian holography and Schwinger--Keldysh methods, meanwhile, make precise
how real-time propagation, contour doubling, and BRST/cohomological structures
enter holographic calculations
~\cite{Schwinger1961,Keldysh1964,SkenderisVanRees2008,SkenderisVanRees:2009RealtimeRenorm,HaehlLoganayagamRangamani:2016SKBRST}.
Local RG work gives a complementary anomaly-based language for Weyl consistency
and flow data~\cite{Osborn1991LocalRG,Nakayama2015LocalRG}.  These developments
organize physical time, RG time, and anomaly structure, but they do not relate a multiplicity of physical times to physical symmetries at all.

On the symmetry side, classification results such as
Coleman--Mandula, Haag--\L opusza\'nski--Sohnius, and Nahm tell us what
extensions of spacetime and conformal symmetry are allowed once suitable odd
generators and Hilbert-space hypotheses are already present
~\cite{ColemanMandula1967,HaagLopuszanskiSohnius1975,Nahm1978}.  Those results
are indispensable for the endpoint of the present argument, but they are
endpoint theorems: they do not explain how a relevant odd generator is created
from bosonic bulk/boundary data, nor how it survives locality, quotient, and
activity constraints.

There is also a substantial literature on emergent supersymmetry at boundaries
and quantum critical points~\cite{GroverShengVishwanath2014,FeiGiombiKlebanovTarnopolsky2016,ZhaoLiu2019}.
That literature is important because it shows that supersymmetry need not be a
microscopic input and because it exhibits nontrivial obstructions to emergence.
Its mechanisms are, however, different from the one studied here: they
typically begin with fermionic degrees of freedom or tuned Yukawa/critical
systems.  Our starting point is instead a purely bosonic two-time setting
equipped with the 2T-Limited Scope odd holonomy obstruction.

A distinct earlier program on two-time physics was developed by Bars and
collaborators, where the second time is controlled by gauge symmetry and
different one-time systems arise as gauge-fixed or ``holographic'' pictures of
a higher-dimensional parent theory~\cite{BarsKounnas1997,Bars2001Survey,Bars2000FieldTheory}.
Within that framework there are explicit field-theoretic, gravitational, and
supersymmetric constructions, including gauge/gravity backgrounds,
\(N=1\) supersymmetric field theories, and superconformal/twistor-string
realizations~\cite{Bars2000GaugeGravityBackgrounds,BarsKuo2007SUSYFieldTheory,BarsKuo2007NOnePRL,Bars2004TwistorSuperstring}.
This line of work is important context for the present paper because it shows
that two-time setups can consistently host rich supersymmetric structure.  Its
mechanism is nevertheless different from ours: the odd or supersymmetric sector
is built into the microscopic two-time framework from the start, whereas here
we ask when a purely bosonic two-time setting is forced to realize a local odd boundary channel with
superconformal closure.

To our knowledge, the missing piece in this landscape is a theorem-level route
from the LS odd holonomy to a local, physically active boundary odd
derivation with superconformal closure on a single UV Hilbert space.  The
companion 2T-LS paper establishes the holonomy side
~\cite{Surdu2TLSLetter2026}.  The present paper studies the realization side:
when and how that \(\mathbb{Z}_2\)-gradedness survives the boundary reduction steps and
becomes symmetry.

\subsection{Our Proposal}

Our proposal is that the LS odd holonomy is not merely a square-loop
obstruction.  In an admissible two-time \(AdS_5\) setting it can be carried all
the way to the UV boundary and realized there as a concrete odd symmetry
channel.  The Main theorem identifies a realization chain with two explicit
selected-line interfaces: a same-tick obstruction package controlling the
square-loop no-extra-collapse step, and a delayed selected-line package
furnishing a nonzero quotient point at the successor ledger step.  RG time
produces the odd descendant class; these selected-line interfaces and the
activity package prevent its collapse or darkness; canonicalization and
Hamiltonization turn it into a local odd derivation; and Hilbert-space plus
common-sector closure produce
Weyl-spinor charges and same-\(\mathcal H\) superconformal symmetry.

In plain language, the paper does not say that any theory with two bosonic
times becomes supersymmetric.  It singles out the narrower class in which RG
time leaves a genuine odd trace, that trace survives quotienting, remains
locally visible, and can actually be promoted to symmetry.  The result is
therefore a criterion for when two bosonic times give rise to a nontrivial odd
boundary channel with superconformal consequences.

The introduction-level roadmap is summarized in Fig.~\ref{fig:intro-roadmap}.
Its nodes name the objects the theorem constructs, while its arrows name the
operations that move from one stage to the next.

\begin{figure}[t]
\centering
\begin{tikzpicture}[
  stage/.style={
    draw,
    rounded corners,
    align=center,
    text width=0.18\textwidth,
    minimum height=1.55cm,
    inner sep=6pt
  },
  flow/.style={-{Latex[length=2.4mm]}, thick},
  flowlabel/.style={font=\scriptsize, align=center, text width=0.19\textwidth}
]
\node[stage] (ls) at (0,0) {LS oddness\\[2pt]
  \footnotesize square-loop sign and nonsplitting holonomy};
\node[stage] (desc) at (4.45,0) {Surviving boundary odd class\\[2pt]
  \footnotesize first descendant \([\Xi^{(1)}]\)};
\node[stage] (delta) at (8.90,0) {Canonical local odd derivation\\[2pt]
  \footnotesize \(\delta=\{\mathcal J^{\mathrm{can}},-\}_{\mathrm P}\)};
\node[stage] (sym) at (13.35,0) {Same-\(\mathcal H\) superconformal symmetry\\[2pt]
  \footnotesize Weyl-spinor odd charges plus conformal closure};

\draw[flow] (ls) -- (desc);
\draw[flow] (desc) -- (delta);
\draw[flow] (delta) -- (sym);

\node[flowlabel] at ($(ls)!0.5!(desc)+(0,-1.75)$)
  {RG production,\\parity transport,\\same-tick obstruction / delayed lift};
\node[flowlabel] at ($(desc)!0.5!(delta)+(0,-1.75)$)
  {canonical selection,\\activity,\\Hamiltonization};
\node[flowlabel] at ($(delta)!0.5!(sym)+(0,-1.75)$)
  {HLS realization\\and common-sector\\closure};
\end{tikzpicture}
\caption{Introduction-level roadmap for the Main theorem.  The nodes indicate
what kind of odd object is available at each stage; the arrows indicate what
the theorem must still do in order to pass to the next stage.}
\label{fig:intro-roadmap}
\end{figure}

Here \([\Xi^{(1)}]\) denotes the odd first-descendant class produced by the RG
interface, \(\mathcal J^{\mathrm{can}}\) its derived canonical
representative, and \(\delta\) the resulting Hamiltonized odd derivation.  Only
this Hamiltonized derivation enters Haag--\L opusza\'nski--Sohnius.

The two bosonic times play fundamentally different roles.  Physical time
organizes real-time propagation, descent, and Ward identities.  RG time
organizes coarse-graining and produces the odd anomaly insertion that the
theorem tracks.  There is no general reason why these two times should yield
odd boundary symmetry.  The theorem isolates the required mechanism: RG time
must produce a genuine odd shadow, and that shadow must survive the relevant
reduction steps and remain active in the even sector.

The theorem excludes theories in which the odd shadow is absent, scheme-trivial, destroyed by the
relevant quotient, or present only as a dynamically dark sector.  This will be
unpacked later in Section~\ref{sec:rg-monotone-good}; for now the important
point is that the theorem identifies a bridge from the LS oddness to
superconformal symmetry, not a universal statement about every two-time model.

The base theorem stops at same-\(\mathcal H\) superconformal closure.  That
endpoint is already strong: the odd charges and conformal generators act on one
and the same UV Hilbert space and close to the full four-dimensional
superconformal algebra.  The stronger claim forcing \(\mathcal N=4\) belongs to
a separate optional criterion with additional assumptions.  It should not be
confused with the base realization theorem.

One further warning already matters at the level of orientation: ghost parity,
physical \(\Gamma\)-parity, and the LS holonomy character \(\omega\) must not be
identified.  Their precise roles are fixed in Section~\ref{sec:setup-body}
before the main statement is given.

Accordingly, the proposal does not assume an initial odd AQFT derivation, a
Hilbert-space odd implementer supplied at the start, Weyl-spinor generators or
superalgebra closure inserted by hand, an a priori superconformal multiplet, or
an identification of the physical-time BRST differential \(Q_t\) with a
microscopic supercharge.

The paper is organized as follows.  Section~\ref{sec:setup-body} formulates the
two-time boundary setting, lays out the relevant failure modes, organizes the
assumption packages by role, and states the main theorem.  Section~\ref{sec:cptp-brst}
then gives the transport chain itself, from the LS sign action to the
Hamiltonized odd derivation.  Section~\ref{sec:UV-fixed-point} separates the
base same-\(\mathcal H\) superconformal closure theorem from the stronger
optional maximality criterion.  Sections~\ref{sec:rg-monotone-good}
and~\ref{sec:discussion} are not afterthoughts: they explain what class of
theories the theorem actually selects, what the LS input contributes inside
that class, why the ledger question matters, and how a microscopic
realization is expected to fit into the broader program.

\section{Setting, assumptions, and main theorem}
\label{sec:setup-body}

We now formulate the theorem as a statement about a generic \(AdS_5\) UV
boundary equipped with two bosonic times.  The assumptions are presented in
package form because the theorem is not a one-step implication.  It begins with
the LS odd holonomy, passes through RG descendant formation and local
selection, and ends only after Hamiltonization and Hilbert-space symmetry
closure have been established.

\subsection{Two bosonic times and one local target}
\label{subsec:two-time-arrows}

We work with a five-dimensional \(AdS_5\) background whose conformal boundary
admits a four-dimensional Lorentzian local quantum field theory on a Minkowski
UV chart.  Physical time \(t\) and radial/RG time \(u\) are treated as two
independent monotonic directions.  Physical time acts through ordinary
Lorentzian evolution.  RG time acts through the radial/Wilsonian direction.
The Schwinger--Keldysh completion is assumed to make both time directions visible on the
same sufficiently local class of boundary observables, so that the analysis can
be carried out inside one local framework.  This common framework is not a
convenience.  If physical time and RG time lived only on different
descriptions, their odd descendants could fail to communicate and the theorem
would have no coherent local target.

Within this framework the SK construction supplies a two-time BRST bicomplex
\((Q_t,Q_u)\) on sufficiently local observables.  The operator \(Q_t\) belongs
to the real-time SK structure and organizes descent and Ward identities.  The
operator \(Q_u\) belongs to the RG direction and is the source of the odd
insertion that the theorem tracks.  The two differentials are therefore not
interchangeable.  The theorem follows the RG-produced odd descendant
\(Q_u^{\mathrm{phys}}\mathcal O^{(0)}\), not the physical-time differential
\(Q_t\) itself.

Next point must be kept sharp: the LS chain bicomplex and the boundary BRST
bicomplex are not identified.  The LS theorem supplies an odd holonomy and a
sign action; the Main theorem shows how that sign action reaches the local
boundary descendant quotient.  Only after parity transport, nonvanishing, and
canonical selection does one obtain the Hamiltonized odd derivation
\(
\delta=\{\mathcal J^{\mathrm{can}},-\}_{\mathrm P}
\)
that enters the Hilbert-space symmetry theorem.

\subsection{Failure modes and package architecture}
\label{subsec:failure-modes-main}

At this stage neither supersymmetry nor a local odd charge is assumed.  The
problem is instead to determine whether the two-time data force a genuine odd
boundary channel with physical content.  Four obstructions can prevent this
from happening:
\begin{enumerate}[label=\textnormal{(\roman*)},leftmargin=*,itemsep=0.25em]
  \item RG time may fail to produce a genuine odd first descendant once
  scheme contributions are removed;
  \item the LS sign action may fail to survive transport into the
  local descendant quotient;
  \item a surviving odd class may remain physically dark, acting trivially on
  all sufficiently local even probes;
  \item even a nontrivial active odd derivation may fail to satisfy the
  locality, covariance, energy, or implementability requirements needed for a
  Hilbert-space symmetry theorem and conformal closure.
\end{enumerate}
The package stack is organized exactly around these failure modes.  One part of
the stack supplies the LS holonomy input, a second part produces and stabilizes the local odd
descendant class, a third part promotes that class to a genuine derivation, and
a final part places the resulting derivation inside the Hilbert-space and
conformal framework where HLS and same-\(\mathcal H\) closure apply.

\subsection{Package synopsis and main statement}
\label{subsec:assumptions-main}

The assumption packages are best read in four gates rather than as one
undifferentiated bundle.
\begin{itemize}
  \item \textbf{LS oddness.}
  The package \(\mathbf{2T}_{\mathrm{LS}}\) supplies the parity cocycle, the
  nonsplitting \(\mathbb Z_2\)-cover, the detector-based distinguishability
  statement, and the square-loop sign action.  This is the oddness that
  the Main theorem attempts to realize on the boundary.

  \item \textbf{Descendant formation.}
  The package \(\mathbf{2T}_{\mathrm{RG}}\) provides an even sufficiently local
  representative \(\mathcal O^{(0)}\), decomposes the RG odd operator into
  physical and scheme parts, and isolates the genuine odd insertion
  \(Q_u^{\mathrm{phys}}\mathcal O^{(0)}\).  Together with
  \(\mathbf{2T}_{\mathrm{char}}^{\mathrm{weak}}\), it places the resulting odd
  data in the affine descendant class \([\Xi^{(1)}_{\Lambda_k}]\) where one can
  ask whether a genuine odd direction survives.

  \item \textbf{Survival and visibility.}
  The supplement \(\mathbf{2T}_{\mathrm{sel}}\) provides the same-tick
  obstruction lane on the abstract selected quotient, while
  \(\mathbf{2T}_{\mathrm{sel}}^{\mathrm{delay}}\) furnishes the delayed
  quotient-first route at the successor ledger step.  Together
  they keep the selected odd channel alive at the right abstract and physical
  interfaces.  The supplement
  \(\mathbf{2T}_{\mathrm{char}}^{\mathrm{act}}\) requires this selected odd
  direction to be visible to at least one sufficiently local even probe, so
  that the surviving odd channel is not physically dark.  The Peierls package
  \(\mathbf{2T}_{\mathrm{Peierls}}\) then converts the selected sufficiently
  local representative into a genuine derivation on observables.

  \item \textbf{Boundary symmetry closure.}
  The energy-bounds/covariance package \(\mathbf{2T}_{\mathrm{EBC}}\) supplies
  the UV locality, covariance, vacuum, and energy-control hypotheses needed for
  AQFT reconstruction and for the verification of the
  Haag--\L opusza\'nski--Sohnius interface.  The conformal common-sector package
  \(\mathbf{2T}_{\mathrm{conf}}\) ensures that the conformal generators and the
  odd charges act on one vacuum representation and one common invariant core,
  so that the odd symmetry sector closes with the \(SO(4,2)\) generators on a
  single Hilbert space.
\end{itemize}

Two structural remarks are crucial.  First,
\(\mathbf{2T}_{\mathrm{char}}^{\mathrm{cal}}\) is not a separate primitive
assumption.  It is derived from
\(\mathbf{2T}_{\mathrm{char}}^{\mathrm{weak}}\) and supplies the Hilbertizing
form used to select the canonical representative
\(\mathcal J^{\mathrm{can}}\).  Second, the BRST, AQFT, and HLS structures are
not independent axioms inserted by hand.  The SK construction supplies the BRST
bicomplex, the UV locality/covariance data supply the AQFT representation, and
the Hamiltonized odd derivation is then shown to satisfy the HLS hypotheses.
The odd derivation and the superconformal algebra are therefore derived
consequences of the package hypotheses.

\begin{remark}[Three \(\mathbb Z_2\) parities (do not mix)]
\label{rem:three-Z2-main}
We keep three distinct \(\mathbb Z_2\) parities throughout the analysis:
\emph{ghost parity} (SK/BRST cohomological degree mod \(2\)),
\emph{physical parity} \(\Gamma\) (an involutive \( * \)-automorphism on the
observable net, defining \(\Gamma\)-even and \(\Gamma\)-odd sectors), and the
\emph{Limited-Scope holonomy} \(\omega\in\mathbb Z_2\) of the procedure cover,
represented on observables by \(\Gamma^\omega\).  Ghost parity is bookkeeping,
whereas \(\Gamma\) and \(\omega\) are physical.  The LS chain bicomplex
\((Q_t^{\mathrm{ch}},Q_u^{\mathrm{ch}})\) and the boundary BRST bicomplex
\((Q_t,Q_u)\) are not identified; they interact only through the
parity-transport step described in Appendix~\ref{sec:parity-bridge}.
\end{remark}

\begin{theorem}[2T-Main theorem, informal]
\label{thm:main}
Consider a generic \(AdS_5\) setup whose UV boundary admits a four-dimensional
local quantum field theory together with the assumption packages
\[
\mathbf{2T}_{\mathrm{LS}}
\;+\;
\mathbf{2T}_{\mathrm{RG}}
\;+\;
\mathbf{2T}_{\mathrm{Peierls}}
\;+\;
\mathbf{2T}_{\mathrm{EBC}}
\;+\;
\mathbf{2T}_{\mathrm{char}}^{\mathrm{weak}}
\;+\;
\mathbf{2T}_{\mathrm{char}}^{\mathrm{act}}
\;+\;
\mathbf{2T}_{\mathrm{sel}}
\;+\;
\mathbf{2T}_{\mathrm{sel}}^{\mathrm{delay}}
\;+\;
\mathbf{2T}_{\mathrm{conf}},
\]
and suppose that the two-time Schwinger--Keldysh construction furnishes the
corresponding BRST bicomplex on sufficiently local observables.  Then the
following statements hold.
\begin{enumerate}[label=\textnormal{(\roman*)},leftmargin=*,itemsep=0.35em]
  \item The RG package produces a genuine odd first-descendant class
  \([\Xi^{(1)}_{\Lambda_k}]\), and the LS square-loop is transported by
  parity to a sign action on its selected quotient image
  \(\overline{\Xi}^{(1)}_{\Lambda_k}\).

  \item The same-tick selected-line supplement provides the obstruction route on
  that abstract quotient, while the delayed selected-line supplement supplies a
  nonzero quotient point at the successor ledger step.  Together
  they provide the nonvanishing input used by the derived calibration package
  to select a unique nonzero canonical odd representative
  \(\mathcal J^{\mathrm{can}}_{\Lambda_k}\in[\Xi^{(1)}_{\Lambda_k}]\).

  \item The activity supplement shows that this canonical odd line is not
  locally dark, and the Peierls bracket Hamiltonizes
  \(\mathcal J^{\mathrm{can}}_{\Lambda_k}\) into a nontrivial local
  \(\Gamma\)-odd derivation
  \[
  \delta_{\Lambda_k}
  =
  \{\mathcal J^{\mathrm{can}}_{\Lambda_k},-\}_{\mathrm P,\Lambda_k}.
  \]

  \item The AQFT and Haag--\L opusza\'nski--Sohnius hypotheses are satisfied by
  this Hamiltonized derivation.  Hence the UV boundary carries a
  finite-dimensional Weyl-spinor odd charge module on the same vacuum
  representation, with indexed generators \(Q_\alpha^I\) and
  \(\bar Q_{\dot\alpha I}\) satisfying
  \[
  \{Q_\alpha^I,\bar Q_{\dot\beta J}\}
  =
  2\,\delta^I{}_J\,\sigma^\mu_{\alpha\dot\beta}P_\mu,
  \qquad
  \{Q_\alpha^I,Q_\beta^J\}
  =
  \{\bar Q_{\dot\alpha I},\bar Q_{\dot\beta J}\}=0;
  \]

  \item Combining the odd charge module with the common conformal sector yields
  the full four-dimensional superconformal algebra on the same Hilbert space.
  More precisely, the resulting operator Lie superalgebra is
  \(\mathfrak{su}(2,2|N)\) for \(N\neq4\), while in the \(N=4\) case the
  standard simple form is obtained after quotienting the central
  \(\mathfrak u(1)\), giving \(\mathfrak{psu}(2,2|4)\).
\end{enumerate}
\end{theorem}

The base conclusion of the theorem is therefore same-\(\mathcal H\)
superconformal closure.  The odd sector is not inserted by hand.  It is
reconstructed from the RG descendant, stabilized by the same-tick obstruction
and delayed selected-line supplements, made dynamically meaningful by activity
and Hamiltonization, and only then promoted to Hilbert-space symmetry by HLS.

This is the natural endpoint of the base realization theorem.  Forcing
\(N=4\) is a separate strengthening problem.  It uses additional structural
assumptions on the UV fixed point and should not be folded back into the
assumption burden of the base theorem.

\begin{proposition}[Strengthened maximality criterion]
\label{prop:main-optional-4c}
Assume, in addition to the hypotheses of Theorem~\ref{thm:main}, that the UV
fixed point is non-gravitational with a unique stress tensor, genuinely
interacting in the sense that the SK RG monotone has a nondegenerate UV
extremum and no decoupled free SCFT sector is present, and carries no
higher-spin enhancement.  Assume also the standard spin-2 saturation input
that a unitary four-dimensional superconformal theory with \(N>4\) and a
unique stress tensor must contain a graviton and therefore cannot occur in the
non-gravitational setting, and assume that interacting non-gravitational
SCFTs exist for each \(N\in\{1,2,3,4\}\).

Finally impose the following \emph{maximality principle}: among
SK-admissible UV fixed points compatible with the same macroscopic data
(dimension, locality, spin range, and the standing two-time structure), the
RG dynamics selects those with the largest available unbroken symmetry.  In
particular, once the allowed superconformal algebras have been reduced to
\(\mathfrak{su}(2,2|N)\) with \(1\le N\le4\), the realized fixed point takes
the largest admissible \(N\); a smaller value of \(N\) cannot be compensated
by adding further continuous symmetries without changing the universality
class.

Then the superconformal multiplicity parameter is forced to be \(N=4\).  This
yields a separate optional criterion for maximal \(\mathcal N=4\)
supersymmetry, as summarized in Proposition~\ref{prop:4c-N-equals-4}.
\end{proposition}

Section~\ref{sec:cptp-brst} now proves the transport-and-realization chain
announced above.  Section~\ref{sec:UV-fixed-point} establishes the exact closure
endpoint and keeps it separate from maximality.  Only after that theorem spine
is in place do Sections~\ref{sec:rg-monotone-good} and~\ref{sec:discussion}
return to the broader interpretive questions: what class of theories is really
being selected, what the LS input contributes inside that class, and what a
concrete ledger realization would have to supply.

\section{From LS holonomy to a boundary odd derivation}
\label{sec:cptp-brst}

The core logic of the theorem is best read as a transport-and-realization
chain.  The LS theorem gives an odd sign action.  The Main theorem shows how
that sign action reaches the selected descendant quotient, forces nonvanishing,
produces a canonical odd representative, and finally becomes a local odd
derivation with symmetry consequences.  Each step removes a distinct
obstruction.

\begin{enumerate}[label=\textnormal{(\arabic*)},leftmargin=*,itemsep=0.55em]
  \item \textbf{LS parity transport.}  The Limited Scope theorem
  provides the square-loop sign action at the record/process level.  This is
  only the beginning.  The Main theorem still has to transport that sign action
  to the boundary descendant sector.  The parity-transport step identifies the
  LS square-loop action with physical parity on first descendants, but this
  transport is meaningful only after one specifies the selected local quotient
  in which the boundary odd channel is to live.

  \item \textbf{RG time produces the odd descendant class.}  The package
  \(\mathbf{2T}_{\mathrm{RG}}\) provides an even sufficiently local
  representative \(\mathcal O^{(0)}\), decomposes the RG odd operator into
  physical and scheme parts, and isolates the genuine odd insertion
  \(Q_u^{\mathrm{phys}}\mathcal O^{(0)}\).  The anomalous descent relation
  \[
  Q_u^{\mathrm{phys}}\mathcal O^{(0)}+Q_t\Xi^{(1)}=\mathcal A^{(1)}
  \]
  is the first place where bosonic RG time produces the odd class
  \([\Xi^{(1)}_{\Lambda_k}]\) used by the theorem.  This is why the theorem
  follows the RG anomaly sector rather than treating \(Q_t\) as the symmetry
  generator.

  \item \textbf{The same-tick obstruction package realizes the LS sign action on
  the abstract selected quotient.}  The supplement
  \(\mathbf{2T}_{\mathrm{sel}}\) isolates a nonzero odd line in the descendant
  ambiguity group and provides the obstruction contract required to transport
  the LS sign action to the selected quotient image
  \(\overline{\Xi}^{(1)}_{\Lambda_k}\).  This is the precise abstract
  bridge from the LS holonomy landscape to the Main descendant quotient.

  \item \textbf{The delayed selected-line package gives the delayed-step
  nonvanishing route.}  The supplement
  \(\mathbf{2T}_{\mathrm{sel}}^{\mathrm{delay}}\) furnishes a nonzero
  quotient point at the successor step together with the
  delayed split-to-descendant map and the separate dominant-response gate.
  This is the physically relevant odd-to-even export interface.  With the
  same-tick obstruction route and the delayed route both present, the odd class
  cannot collapse away before canonicalization.

  \item \textbf{The nonzero class yields a canonical odd representative and a
  local odd derivation.}  The derived calibration supplement supplies the
  Hilbertizing form needed to choose the unique norm-minimizing representative
  \(\mathcal J^{\mathrm{can}}_{\Lambda_k}\in[\Xi^{(1)}_{\Lambda_k}]\).  The
  activity supplement then guarantees that this distinguished odd direction is
  not locally dark.  The Peierls package Hamiltonizes it to
  \[
  \delta_{\Lambda_k}
  =
  \{\mathcal J^{\mathrm{can}}_{\Lambda_k},-\}_{\mathrm P,\Lambda_k}.
  \]
  This is the point at which the odd content stops being a quotient class and
  becomes a local odd derivation on observables.

  \item \textbf{HLS promotes the Hamiltonized derivation to a Weyl-spinor odd
  charge module.}  The energy-bounds/covariance package, together with the UV
  locality data, places the theory in the setting where AQFT reconstruction and
  Haag--\L opusza\'nski--Sohnius apply.  HLS does not act on \(Q_t\); it acts on
  the Hamiltonized derivation \(\delta\).  The conclusion is a
  finite-dimensional Weyl-spinor odd charge module with indexed generators
  \(Q_\alpha^I\) and \(\bar Q_{\dot\alpha I}\).

  \item \textbf{The odd charge module closes with the conformal sector on the
  same Hilbert space.}  The conformal common-sector package ensures that the
  conformal generators and the odd charges act on one vacuum representation and
  one common invariant core.  The result is same-\(\mathcal H\)
  superconformal closure.  Only after this base closure theorem is in place
  does it make sense to ask whether stronger assumptions force \(N=4\).
\end{enumerate}

Two remarks summarize the mechanism.  First, the theorem’s central generator is
not \(Q_t\) but \(\delta\).  The role of \(Q_t\) is to organize descent and Ward
identities.  Second, the same-tick obstruction supplement, the delayed
selected-line supplement, and the activity supplement solve different problems.
The first gives the abstract no-extra-collapse route, the second gives the
quotient route through the successor ledger step, and the third prevents the surviving odd
channel from remaining physically dark.  The logic is therefore rigid:
removing any one of these steps breaks a different part of the chain.

\section{Superconformal closure versus maximality}
\label{sec:UV-fixed-point}

The intrinsic endpoint of the base theorem is same-\(\mathcal H\)
superconformal closure.  This means that the conformal generators inherited
from the \(AdS_5\) boundary geometry and the odd generators obtained from the
Hamiltonized descendant sector act on one and the same UV Hilbert space.  The
result is already strong: it is not merely the existence of an odd charge
module, but the closure of that module with the full four-dimensional
conformal algebra.

At this stage the theorem yields the precise distinction
\[
\mathfrak{su}(2,2|N)\quad (N\neq4),
\qquad
\mathfrak{psu}(2,2|4)\quad (N=4).
\]
For \(N=4\) the simple superalgebra is obtained only after quotienting the
central \(\mathfrak u(1)\), which is why the natural final form is
\(\mathfrak{psu}(2,2|4)\).

This closure theorem is already substantial even before any maximality claim
is made.  It says that the odd channel reconstructed from the RG descendant is
not an isolated algebraic artifact; it integrates coherently with the full
four-dimensional conformal symmetry on the physical UV Hilbert space.

It is mathematically essential to separate this closure theorem from the
stronger criterion forcing \(N=4\).  The stronger criterion uses additional
assumptions: non-gravitationality, spin-2 saturation, interaction, absence of
higher-spin enhancement, and the existence and maximality conditions recorded
in the strengthening analysis.  These assumptions restrict the UV fixed point in ways that go beyond the
odd-channel realization problem itself.

For this reason the theorem naturally has two layers of conclusion.
\begin{enumerate}[label=\textnormal{(\roman*)},leftmargin=*,itemsep=0.35em]
  \item The base theorem yields same-\(\mathcal H\) superconformal closure and
  determines the superconformal algebra up to the multiplicity parameter
  \(N\).
  \item The strengthened maximality criterion imposes additional structural
  assumptions and then forces \(N=4\).
\end{enumerate}

These layers provide clear distinction in assumption burden so the logical structure of the result is transparent.

\section{Physical meaning and scope}
\label{sec:rg-monotone-good}

\subsection{What class of theories is selected?}

These assumptions do not single out
``supersymmetric theories'' in any direct or circular way.  What they single
out is a narrower and more precise class: theories in which the bosonic
two-time structure supports a nontrivial odd shadow that survives all
reduction steps and remains physically active on the UV boundary.  The
restrictive assumptions are therefore concentrated in three places: the RG
package, the selected-line supplement, and the activity supplement.

\begin{enumerate}[label=\textnormal{(\arabic*)},leftmargin=*,itemsep=0.4em]
  \item \textbf{The theorem excludes a purely bosonic RG sector.}  If the RG
  monotone can be
  described, after removing scheme terms, without a genuine odd insertion
  \(Q_u^{\mathrm{phys}}\mathcal O^{(0)}\), then the theory lies outside the
  admissible class.  The point is not that every bosonic theory is ruled out,
  but that the class treated here must have an odd cohomological shadow
  attached to its RG time.

  \item \textbf{The theorem excludes a scheme-trivial odd shadow.}  If the odd
  RG insertion is
  killed by \(Q_t\)-exactness or can be absorbed entirely into scheme
  redefinitions, then the odd channel carries no invariant physical content and
  the theorem does not apply.  Thus the odd descendant must encode more than a
  bookkeeping artifact of the renormalization scheme.

  \item \textbf{The theorem excludes collapse before the local descendant
  quotient.}  If a candidate odd line
  exists only in a coarser raw packet but dies when one passes to the
  descendant quotient, then the relevant selected-line package fails: either
  the same-tick obstruction route \(\mathbf{2T}_{\mathrm{sel}}\) is not
  available on the abstract selected carrier, or the delayed route
  \(\mathbf{2T}_{\mathrm{sel}}^{\mathrm{delay}}\) does not produce the
  quotient point at the successor ledger step.  The theorem therefore requires not just
  abstract odd data, but odd data that survives the precise quotient procedure
  relevant to the local boundary theory.

  \item \textbf{The theorem excludes a physically dark odd sector.}  If the
  selected odd line
  survives abstractly but acts trivially on every even sufficiently local
  probe, then \(\mathbf{2T}_{\mathrm{char}}^{\mathrm{act}}\) fails and the
  theory is excluded.  This is a minimal nondegeneracy requirement: the odd
  direction must be dynamically visible somewhere in the local even sector.
\end{enumerate}

The physical slogan is therefore the following.  The theorem applies to
theories in which bosonic RG time produces a genuine odd descendant, one
selected odd component survives the ambiguity and collapse steps, and that
surviving component is detectable through local even observables.  This is a
considerable restriction, but it is still weaker than assuming a fermionic symmetry
from the outset.

The selected class may therefore be described as proto-fermionic rather than
supersymmetric in the usual input sense.  These theories are distinguished not
because they begin with a supercharge, but because their two-time structure is
rich enough to support an odd sector that remains stable under all the
physically relevant reductions and can no longer be ignored dynamically.

\subsection{What does the LS input do inside the selected class?}

Entering the admissible class, the LS input supplies the physical picture of two times in our paradigm.  It introduces a \emph{classical ledger of
records}, a reversible microscopic time evolution between ledger checkpoints,
and an \emph{RG/coarse-graining operation that forgets fine-grained information} returning the world to the ledger point.  These two times are
ledger-mediated: one carries microscopic evolution between checkpoint, while the other changes how much of that evolution survives in the
recorded history.

LS then isolates the key fact about the interaction of these two times.  A
ledger by itself is not enough: if everything microscopic were already fixed by
the visible record, then ``live, then forget'' and ``forget, then live'' would
be the same story in two notations.  But the two-time square to be genuinely
nontrivial; it means there must be a \emph{completion sector} beyond the ledger, carrying
microscopic information that is not recorded at the checkpoint.

On the ledger itself, the square still closes: the same endpoint record can be
reached either way.  But one must also specify how the unrecorded microscopic
completion data are attached to that common corner.  That completion rule is
what LS calls a \emph{filler}.  LS singles out two canonical fillers, and their
difference is exactly the physical point: they agree on the same visible ledger
step, so they must be invisible there, yet they are not the same microscopic
realization.  Their mismatch survives in the completion sector as an
irreducible \(\mathbb Z_2\) sign.  That sign is objective.  It is not a matter
of notation, state relabeling, or endpoint bookkeeping.

LS does not select the theory class. Instead, it provides the underlying source of oddness: a genuine mismatch
between two filler-related microscopic completions of one and the same visible
ledger history.  Main then asks for the narrower class in which this hidden
completion-sector difference survives the reduction chain and reaches the UV
boundary as an active odd channel.

\subsection{But what is the ledger?}
\label{subsec:what-is-ledger}
The ledger is not the full microscopic state.  It is the accepted classical
record sector: the commuting facts that survive coarse-graining and define what
counts as the same visible history at a checkpoint.  Abstractly, what these records are made of can be ignored.  We use only the
structural claim that such a classical record layer exists and is rich enough so the Universe can perform RG/CPTP coarse-graining step, and that the completion sector carries the microscopic data that the ledger forgets.

These abstract claim level have considerable implications from 2T-LS and 2T-Main. 
\begin{itemize}
\item Wheeler's slogan ``it from bit'' becomes theorem-level statement~\cite{Wheeler1990ItFromBit};
\item $\mathbb{Z}_2$-gradedness surfaces in two deeply linked appearances:
\begin{itemize}
  \item objective distinction between before and after \emph{compatible with unitary evolution}; hence the real arrow of time that circumvents the hard wall of the constant von Neumann entropy.
  \item \emph{spinor symmetry} originating at the UV boundary; hence existence of the matter-rich Universe.
\end{itemize}
\item confluence of two appearances at a conformal boundary, conjecturally producing IIb microscopic theory in the standard $AdS_5/CFT_4$ setup.
\end{itemize}

This is why the ledger question matters so much.  If nature really contains
such a classical record layer, then the same structure would underwrite the whole chain from highest-level principle to microscopic theory.  

The present article stops one step short of identifying the ledger concretely.  That is a cosmology theory
question, and it is deferred to the discussion.

\section{Discussion}
\label{sec:discussion}

\subsection{Toward a cosmology realization}

A concrete answer to the ledger question requires a source theory that identifies, in one microscopic
construction, the record sector, the forgetting/coarse-graining operation, and the
completion data whose mismatch carries the LS sign.  

One proposed theory constructs ledger as a Weyl anomaly floor sector of a pure vacuum Karch-Randall \(AdS_4\) brane, which acts as a receiver that accumulates Brown-York flux from the incoming zero-area repeating pulses so that brane is physically holographically renormalized to a higher cutoff, moving in radial direction. 
\footnote{The governing principle is the least SK influence action that is uniquely minimized with the information export pulses of the temporally/spatially LoG/LoG shapes and receiver cutoff-bandlocked widths.}

The remaining anomaly floor is (a) classical, in the sense of being a local function on the brane and not an interacting field, and (b) preserves already stored facts due to widths band-locking. \footnote{Notably, \(AdS_5\) with three spatial dimensions is the minimal space which can contain a ledger of this type: even-\(d\) spaces does not contain a Weyl anomaly, while \(AdS_3\) anomaly floor is not a proper physical information storage, but rather a gauge/bookkeeping direction, and it explains how dimension-independent \(\mathbb{Z}_2\)-gradedness is realized in spinor symmetry only at \(d \ge 3\).}
A Fisher-odd direction feeds complementary sector that carries the odd completion residue not visible in the current
reduced receiver. Such a split af action into receiver wall-move, anomaly floor influx, and completion sector update makes two latter targets independent: the two filler-related
realizations in the completion sector remain indistinguishable in the receiver anomaly floor imprint. 

However, unlike the ledger, the completion sector influx is affine and bears increasing cost, so eventually the real wall-moving solution ceases to exist and completion/receiver complex splits.
In this split, that completion sector becomes the newborn source \(dS_4\) brane. \footnote{\emph{Source} here means that the oddness of completion sector surfaces as a brane coherence stock created by the split that feeds the next receiver due to QND-type leaks to the \(dS_4\) canonical commutant, which is geometrically situated between source and receiver branes along with the new completion sector.}

This sequence is CCC-like: the chain of \(dS_4\) observable Universes with an approximately conformal inheritance. Its ledger step is \emph{aeon}: the period from pre-split to pre-split finals of Universes, when the source coherences is maximally exhausted. So the accumulated \(\mathbb{Z}_2\) difference is eventually read and appears in the
ledger, but on the \emph{next step}.  This is the \emph{delayed zig-zag} picture: invisible on the current ledger, carried
through the completion sector, and first readable at the next receiver. Such a picture can be understood as a rough mirror of the 2T-LS ledger requirement: it provides the concrete physical mechanism by which two times mix and create the true holonomy over history.

Readers who want the full implementation package, including the 2T-LS and 2T-Main interface implementations,
exact audit reports, and 2T-LS formal proof in Agda, should consult the
archival workspace release~\cite{TwoTimesWorkspace2026}.

\subsection{Outlook}

In the light of 2T-Main results, several directions are proposed.  
\begin{enumerate}
  \item Obvious direction is strenghtning of the optional $\mathcal{N}=4$ step. It is expected that one could be resolved on the level of an implementation theory, hence search for such a theory can solidify the vertical chain proposed in Section \ref{subsec:what-is-ledger}.
  \item Another direction is strengthening of Main proof strategy. Currently, the post-Haag--\L opusza\'nski--Sohnius same-\(\mathcal H\) conformal closure step is existential only. Envisioned post-HLS transfer theorem could show that the package \(Q,\bar Q,S,\bar S\) itself is induced from the reduced data of implemention theory+2T-Main.
  \item Finaly, and this direction could be partially following from the first one, the post-HLS rigidity theorem could show that after transfer there is no hidden modulus beyond the candidate sign involution.
\end{enumerate}

If such a program is finished, we could state that the microscopic-level Universe is \(\mathbb{Z}_2\)-lift of its own history, accepted to the ledger.

The main conclusion, however, is already clear.  In the presence of the
assumption packages described above, two bosonic times can do more than generate an abstract odd holonomy.  They can force that oddness into a
surviving, locally effective boundary channel, and that channel can be
promoted to a superconformal symmetry algebra on the UV Hilbert space.

That is the sense in which the result should be read.  It is not a universal
statement about every theory with two times, and it is not a
hidden assumption of supersymmetry in alternative language.  It is a
structural theorem identifying a precise bridge from bosonic two-time data to
odd boundary symmetry.  Once that bridge exists, the symmetry consequences are
far more rigid than the microscopic starting point would have suggested.

\appendix
\IfFileExists{appendix_main.tex}{%
  \input{appendix_main}%
}{%
  \IfFileExists{Main/appendix_main.tex}{%
    \input{Main/appendix_main}%
  }{%
    \input{../Main/appendix_main}%
  }%
}
\clearpage
\IfFileExists{appendix_subprograms_4a-4b.tex}{%
  \input{appendix_subprograms_4a-4b}%
}{%
  \IfFileExists{Main/appendix_subprograms_4a-4b.tex}{%
    \input{Main/appendix_subprograms_4a-4b}%
  }{%
    \input{../Main/appendix_subprograms_4a-4b}%
  }%
}
\clearpage
\IfFileExists{appendix_subprograms_4c_discussion.tex}{%
  \input{appendix_subprograms_4c_discussion}%
}{%
  \IfFileExists{Main/appendix_subprograms_4c_discussion.tex}{%
    \input{Main/appendix_subprograms_4c_discussion}%
  }{%
    \input{../Main/appendix_subprograms_4c_discussion}%
  }%
}

\bibliographystyle{apsrev4-2}
\IfFileExists{refs.bib}{%
  \bibliography{refs}%
}{%
  \IfFileExists{Main/refs.bib}{%
    \bibliography{Main/refs}%
  }{%
    \bibliography{../Main/refs}%
  }%
}

\end{document}
